\section*{Introduction}
\pagenumbering{arabic}
\setcounter{page}{12}
\phantomsection

Time-lapses are used in various domains. Some people want to study a natural phenomena, some want to have an overview on how a city has evolved over the years and others simply want to see how something was built. Some of the more advanced cases are when scientists want to take a picture of a particle at a very high speed, which emits light for a very short time, so a combination of time-lapse with a high exposure is used to create a sketch of what it looks like, to at least help the scientists in the early stage.

No matter the case, the quality requirements are usually extremely high, therefore a DSLR Camera is usually used for this purpose. But these cameras are usually very expensive, so nobody is really thinking about leaving them with no supervision for more than a day, even less people are thinking about making a tool to manage year long time-lapses and even less people are thinking how to easily scale, allowing the photographer to manage hundreds of time-lapses at once with no headache.

Setting up a time-lapse is not too hard. It is usually required to connect the camera to a computer, install the camera specific software, configure it and start taking photos. At the end of the time-lapse, the user usually drag and drops the photos in a special editor and it is done. This works perfectly for 1-2 day long time-lapses, where the user can sit near the camera an manage everything, or when the cost of failure is very low. But this gets extremely tedious when the same software is used for year long time-lapses. Different problems start to appear, like storage failure, camera disconnection, electricity cut off and more. This only gets worse when the user needs a few dozens of such time-lapses to run at the same time.

The goal of this thesis is to create a tool where users can set up a time-lapse and forget about its existence for the next few years, only getting occasional emails when something fails. Why it is important to have such a product on the market? Because there isn't one present. Or those that exist support only a specific model of camera, or offer no API for automation.

\clearpage